Investigating the Impact of Macroeconomic Indicators on the FTSE 250 Index Using Machine Learning Methods

### 2024-08-11 tex/paper.tex
update

One of the earliest papers investigating the effect of money supply on the stock market price was Palmer (1970), who examined the effect of M1 money supply on the S$\&$P 425 Industrial Stock Index and found that ‘primary changes (defined as a trend occurring over a period of
months) in the nation's money stock may motivate the private sector to adjust its wealth portfolios in such a manner as to yield predictable movements in the prices of corporate securities,’ positing a definite relation between the money supply and stock market price. Further research by Homa and Jaffe (1971) indicated that the price of a common stock is determined significantly by the risk-free rate of interest, which itself, according to the liquidity preference theory of the monetarist school of economics, a function of money supply, as more money circulating in the economy means more liquidity available for banks, thus affecting the cost of borrowing (interest) - source -. They found that the money supply has a positive impact on the average level of stock prices. This was disputed by Pesando (1974) who claimed that the inability of the model used in this study to produce accurate forecasts of the stock price was sufficient evidence against a relationship between the money supply and stock market prices. Baks and Kramer (1999), supported by Conover et. al (1999) findings, initially found significant evidence of the impact of money supply on stock markets across G-7 countries:  Canada, France, Germany, Italy, Japan, the UK and the US. This empirically supports the economic theory that increases in money supply generally raise the value of personal asset portfolios, which leads individuals to reallocate excess cash to stocks, in turn affecting stock prices. In the face of the drastic shock to the global economy in 2008, many central banks including the USCB and the Bank of England utilised Quantitative Easing (QE) for the first time. As a macroeconomic tool, QE involves the creation of digital money by the central bank to engage in large-scale asset purchasing to stimulate the economy - stock and other asset markets would theoretically be affected immediately by such a policy. Picha (2017) utilised a portfolio balance model to investigate the effect of QE, measured by the M2 money supply, on the S$\&$P 500 using Johansen’s cointegration methodology and found that the money supply indeed exerted a effect on the latter, and the fact that the adjustment to the long-run equilibrium took 6-months suggested that it was quite moderate. Moreover, cointegration between the money supply and S$\&$P 500 over the long-run was established, adding to a large extant literature that supports long-run dependence of stock price on money supply. Included are Mukherjee and Naka (1995), Wongbangpo and Sharma (2002) and Lee (2006) who posit the long-run dependence of Japanese, New Zealand and ASEAN-5 indices respectively on the M1 money supply; furthermore, Bahloul et. al. (2016) establish that M3 money supply significantly influences developed stock indices such as the UK, USA, and Japan over the long-run. Synek (2024) found long term dependence of stock indices such as the FTSE100 and TSX on the M2 money supply.

@@

For all of the research, monthly data between October 1992, when the FTSE250 index first opened, and March 2024 was utilised. 
To account for the fact that the Bank of England’s Monetary Policy Committee does not meet on a monthly basis, the interest rate data was 
adjusted using the following recipe:
\begin{enumerate}
    \item If the interest rate was unchanged through the month, the previous set rate was used.
    \item If the rate changed from $i_1,\ldots,i_n$ on day $d_j$, for $1\leq j\leq n$ of a month with $x$ days, then a weighted average $W_{int}$ was calculated using (1) - insert hyperlink - to more accurately account for the effects of the interest rate over the month. 
    \item The value of INT in would accordingly be $W_{int}$ for those months in which the rate changed. 
\end{enumerate}

@@

\begin{table}[h!]
    \centering
    \caption{Data sources}
    \begin{tabular}{lll}
        \toprule
        \textbf{Variable} & \textbf{Notation} & \textbf{Source} \\
        \midrule
        FTSE 250 Index & FTSE$_{250}$ & Yahoo Finance (link) \\
        Consumer Price Index & CPI & Office for National Statistics (ONS) (link) \\
        USD/GBP Exchange Rate (£) & EXCHG & Federal Reserve of St Louis (link)\\
        Interest Rate ($\%$) & INT & Bank of England (link) \\
        Money Supply (M3) (millions £) & M3 & Bank of England (link) \\
        \bottomrule
    \end{tabular}
\end{table}

Randomtext
Randomtext
Randomtext
Randomtext
Randomtext
RandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext

Table 2 displays some basic descriptive statistics on the raw data. 
Insert analysis of descriptive statistics and historical behaviour, 
brief notes on why the indicators are relevant

\begin{table}[h!]
    \centering
    \caption{Descriptive statistics}
    \begin{tabular}{lllll}
        \toprule
        \textbf{Variable} & \textbf{Mean} & \textbf{SD} &  \textbf{Min.} & \textbf{Max.}\\
        \midrule
        FTSE 250 Index &  1 & 1 & 1 & 1 \\
        CPI Index &  1 & 1 & 1 & 1 \\
        USD/GBP Exchange Rate &  1 & 1 & 1 & 1 \\
        Interest rate &  1 & 1 & 1 & 1 \\
        Money Supply (M3) &  1 & 1 & 1 & 1 \\
        \bottomrule
    \end{tabular}
\end{table}

Sample size discussion

RandomtextRandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
RandomtextRandomtextRandomtextRandomtext
\section{ARDL Model}

@@

\begin{table}[h!]
    \centering
    \caption{Coefficients Estimates}
    \begin{tabular}{llll}
        \toprule
        \textbf{Variable} & \textbf{Long-Run Coefficient} & \textbf{Variable} & \textbf{Short-Run Coefficient} \\
        \midrule
        FTSE$_{250}$ & N/A & FTSE$_{250}$ $(-5)$  & $-0.033089$ \\
        CPI & $3.157179$ & CPI $(-4)$ & $-0.921235$ \\
        INT & $-0.1341097$ & INT $(-7)$ & $-0.034572^{****}$\\
        EXCHG &  $-0.890146$ & EXCHG $(-7)$ & $0.122318$ \\
        M3 & $-0.1141114$ & M3 $(-4)$ & $-0.527798^{***}$ \\
         & & ECT $(-1)$ & $-0.002$ \\
        \bottomrule
    \end{tabular}
\end{table}

@@

@@

where $r = \|\boldsymbol{\mathrm{x}} - \boldsymbol{\mathrm{c}}\|$ is the Euclidean distance between the input vector 
\(\boldsymbol{\mathrm{x}}\) and the center of the basis function 
\(\boldsymbol{\mathrm{c}}\). The constant $\sigma$ represents the
spread of the basis function at each centre.
-

An image of the network should be added, include courtesy of Bishop.

@@

The methodology should include a reference to the ARDL test
so that we are linking everythnig together, and then go through why we must normalise the data for the RBF
- one of the papers in my bookmarks talks about this. After this it should 
go through how this was implemented in Python, and how we calculated the
optimum hyperparameters, and which test error metric we utilised. Also explain
the long-term and short-term prediction part.

@@

Present the results for the long term and short

@@

What did this study achieve?
How may it inform policymakers and investors?
Areas for future work to build upon.
\bibliographystyle{plainnat}
\bibliography{references}

>>>>

One of the earliest papers investigating the effect of money supply on the stock market price was Palmer (1970), who examined the effect of M1 money supply on the S$\&$P 425 Industrial Stock Index and found that ‘primary changes (defined as a trend occurring over a period of
months) in the nation's money stock may motivate the private sector to adjust its wealth portfolios in such a manner as to yield predictable movements in the prices of corporate securities,’ positing a definite relation between the money supply and stock market price. Further research by Homa and Jaffe (1971) indicated that the price of a common stock is determined significantly by the risk-free rate of interest, which itself, according to the liquidity preference theory of the monetarist school of economics, a function of money supply, as more money circulating in the economy means more liquidity available for banks, thus affecting the cost of borrowing (interest) - source -. They found that the money supply has a positive impact on the average level of stock prices. This was disputed by Pesando (1974) who claimed that the inability of the model used in this study to produce accurate forecasts of the stock price was sufficient evidence against a relationship between the money supply and stock market prices. Baks and Kramer (1999), supported by Conover et. al (1999) findings, initially found significant evidence of the impact of money supply on stock markets across G-7 countries:  Canada, France, Germany, Italy, Japan, the UK and the US. This empirically supports the economic theory that increases in money supply generally raise the value of personal asset portfolios, which leads individuals to reallocate excess cash to stocks, in turn affecting stock prices. In the face of the drastic shock to the global economy in 2008, many central banks including the USCB and the Bank of England utilised Quantitative Easing (QE) for the first time. As a macroeconomic tool, QE involves the creation of digital money by the central bank to engage in large-scale asset purchasing to stimulate the economy - stock and other asset markets would theoretically be affected immediately by such a policy. Picha (2017) utilised a portfolio balance model to investigate the effect of QE, measured by the M2 money supply, on the S$\&$P 500 using Johansen’s cointegration methodology and found that the money supply indeed exerted a effect on the latter, and the fact that the adjustment to the long-run equilibrium took 6-months suggested that it was quite moderate. Moreover, cointegration between the money supply and S$\&$P 500 over the long-run was established, adding to a large extant literature that supports long-run dependence of stock price on money supply. In the same study, it was found that there did not exist a significant relationship between the money supply and the UK stock market. Included are Mukherjee and Naka (1995), Wongbangpo and Sharma (2002) and Lee (2006) who posit the long-run dependence of Japanese, New Zealand and ASEAN-5 indices respectively on the M1 money supply; furthermore, Bahloul et. al. (2016) establish that M3 money supply significantly influences developed stock indices such as the UK, USA, and Japan over the long-run. Synek (2024) found long term dependence of stock indices such as the FTSE100 and TSX on the M2 money supply.

@@

For the scope of this research, monthly data spanning from October 1992—marking the inception of the FTSE 250 index—through to March 2024 has been utilised, giving us 
altogether a dataset of 379 observations.

During the data collection process, it was necessary to deal with an issue raised by the fact that the Bank of England’s Monetary Policy Committee (MPC) does not convene on a monthly basis, and are not obligated to announce a rate on a regular basis. Thus, it was imperative to address the resulting irregularities in the interest rate data; to ensure a more accurate representation of interest rate fluctuations over time, the data was adjusted using the following algorithm:
\begin{enumerate}
    \item If the interest rate was unchanged through the month, the previous set rate was used.
    \item If the rate changed from $i_1,\ldots,i_n$ on day $d_j$, for $1\leq j\leq n$ of a month with $x$ days, then a weighted average $W_{int}$ was calculated using (1) - insert hyperlink - to more accurately account for the effects of the interest rate over the month. 
    \item The value of INT would accordingly be $W_{int}$ for those months in which the rate changed. 
\end{enumerate}

@@

\begin{table}[h!]
    \centering
    \caption{Data sources}
    \begin{tabular}{lll}
        \toprule
        \textbf{Variable} & \textbf{Notation} & \textbf{Source} \\
        \midrule
        FTSE 250 Index & FTSE$_{250}$ & Yahoo Finance \\
        Consumer Price Index & CPI & Office for National Statistics (ONS) \\
        USD/GBP Exchange Rate (£) & EXCHG & Federal Reserve of St Louis \\
        Interest Rate ($\%$) & INT & Bank of England \\
        Money Supply (M3) (millions £) & M3 & Bank of England \\
        \bottomrule
    \end{tabular}
\end{table}

Table 1 presents the sources of the data; the original datasets are available on request. 
The precedent for the selection of these variables as some of the most important 
factors in the fluctuation of the stock market has already been set in the literature, however, 
a brief explanation of why the M3 measure of the money supply was chosen is 
required. The M3 measure includes a broader range of liquid assets 
compared to M2, encompassing all the components of M2 plus large time 
deposits, institutional money market funds, and other larger liquid assets
making it a more comprehensive indicator of the money supply's impact on economic activity and financial markets.

\begin{table}[h!]
    \centering
    \caption{Descriptive statistics}
    \begin{tabular}{lllll}
        \toprule
        \textbf{Variable} & \textbf{Mean} & \textbf{SD} &  \textbf{Min.} & \textbf{Max.}\\
        \midrule
        FTSE 250 Index &  11,013 & 6,162 & 2,520 & 24,102 \\
        CPI Index &  88.4 & 18.0 & 62.8 & 134 \\
        USD/GBP Exchange Rate (£) &  0.659 & 0.085 & 0.483 & 0.883 \\
        Interest rate ($\%$) &  3.21 & 2.52 & 0.1 & 8.4 \\
        Money Supply (M3) (millions £) &  1,861,958 & 971,112 & 494,181 & 3,704,873 \\
        \bottomrule
    \end{tabular}
\end{table}

Over the period covered by our dataset, the FTSE 250 index has demonstrated substantial volatility with an average value of 11,013.27, fluctuating between 2,519.9 and 24,102.2. 
This volatility reflects significant market shifts driven by events such as the 
Dotcom bubble burst in 2000, the global financial crisis of 2008, and more recent geopolitical uncertainties such as Brexit, the COVID-19 pandemic, and the Russia-Ukraine conflict. However, 
despite these fluctuations, the index has shown considerable growth, 
indicative of a generally upward trend in the UK stock market over the 
long term.

The USD/GBP exchange rate has exhibited moderate variability, 
ranging from 0.4831 to 0.8834, suggesting periods of both 
appreciation and depreciation of the Sterling. The little variability 
there is can be
attributed to major events such as the 2008 financial crisis and Brexit, 
which both greatly affected the value of the Pound.

The Consumer Price Index (CPI), with an average of 88.36, has 
experienced significant inflationary fluctuations, ranging from 
62.8 to 133.5. These fluctuations highlight varying price levels and 
reflect periods of both high inflation, particularly in the late 2000s 
near the global financial crisis, and also during 2021-22 as the Russia-Ukraine
conflict destabilised energy and food markets, immediately after the devastation 
of supply chains by the COVID-19 pandemic; and also low inflation in the 
years of austerity in the UK and the global recession that onset during 
the COVID19 pandemic.

Interest rates, averaging $3.21\%$, have varied widely from $0.1\%$ to $8.4\%$, with a standard deviation of $2.52\%$, reflecting the 
increasing role of monetary policy in the UK. The Bank of England was forced to adjust interest rates 
many times in response to worsening economic conditions, examples being the steep rate cuts during the 2008 crisis to stimulate the economy and the gradual rate hikes in response to subsequent inflationary pressures.

The money supply (M3), averaging 1,861,958.47, has shown substantial variability, ranging from 494,181 to 3,704,873, 
in large part influenced by the various Quantitative Easing (QE) programs implemented by the Bank of England 
in response to the aforementioned crises. These programs aimed to inject liquidity into the economy, thus inflating the overall money supply.

\section{ARDL Model}

@@

\begin{table}[h!]
    \centering
    \caption{Coefficients Estimates}
    \begin{tabular}{llll}
        \toprule
        \textbf{Variable} & \textbf{Long-Run Coefficient} & \textbf{Variable} & \textbf{Short-Run Coefficient} \\
        \midrule
        FTSE$_{250}$ & N/A & FTSE$_{250}$ $(-5)$  & $-0.033089$ \\
        CPI & $3.157179$ & CPI $(-4)$ & $-0.921235$ \\
        INT & $-0.1341097^{**}$ & INT $(-7)$ & $-0.034572^{****}$\\
        EXCHG &  $-0.890146^{***}$ & EXCHG $(-7)$ & $0.122318$ \\
        M3 & $-0.1141114$ & M3 $(-4)$ & $-0.527798^{***}$ \\
        Intercept & $-3.447767$ & ECT $(-1)$ & $-0.16^{**}$ \\
        \bottomrule
    \end{tabular}
\end{table}

@@

The long term coefficients show that the interest rate and exchange rate
interest rate have significant long term effects on the stock market price
while money supply and inflation are statistically insignificant. Neifar (2023) 
proposes that this is because deflation, that is the negative movements in the 
CPI, is a statistically significant factor in the movement of the UK stock 
market, but positive movements (inflation) are not. Nevertheless, the positive
coefficient of 3.16, and the negative short-term adjustment, is in line with the expectation from the literature that 
inflation exerts a positive effect on the stock market in the long-term, but a negative 
one in the short-run.

The insignificant long-term effect of the money supply 
was noted by Picha (2017) and appears to be confirmed here. There are a few explanations
for why this may be.

Unsurprisingly, the USD/GBP exchange rate is significantly related to the FTSE 250's movements. It 
should not be forgotten that, although it is considered to be a more domestic indicator of the LSE, 
at times $50\%$ of the FTSE 250's earnings have come from abroad, indicating that 
the value of the Pound has an important impact on this stock market. As the USD has been 
the global reserve currency for many decades, the depreciation of the Pound 
against it by $1\%$ has an impact of $-0.89\%$ on the FTSE 250. The findings 
are in line with Neifar (2023), Liang and Willett (2015), and Khan and Khan (2018).

The interest rate was also found to have significant negative long-run effects on the 
stock market, affirming the findings of the extant literature ().
The mechanisms by which this occurs were discussed earlier in the literature review.

Turning to the short-run dynamics, we find that the error correction term 
is negative and statistically significant ensuring that long-run equilibrium 
can be achieved. The adjustment speed of $0.16$ indicates that 
roughly $16\%$ of the fluctuation in the previous month's price, caused by the 
macroeconomic variable movements, is adjusted back to the long-run equilibrium in the current month.
However, only increases in the interest rate and money supply are able to 
significantly contribute towards this correction, with $1\%$ increases in the former 
leading to a $-0.03\%$ change in the FTSE250 price 7-months later, and in the case of the latter
a $-0.53\%$ change after a 4-month lag.

@@

where $r = \|\boldsymbol{\mathrm{x}} - \boldsymbol{\mathrm{c}}\|$ is the Euclidean distance between the input vector 
\(\boldsymbol{\mathrm{x}}\) and the center of the basis function 
\(\boldsymbol{\mathrm{c}}\). The constant $\sigma$ represents the
spread of the basis function at each centre.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{bishopnn.png}
    \caption{Courtesy of C. Bishop (1995)}
    \label{fig:bishopnn}
\end{figure}

@@

The ARDL Bounds Test confirmed that our variable selection was sensible by virtue
of its establishment of cointegration. The RBF-NN, it is hoped, will be able
to capture intricate non-linear patterns in the data that the econometric model
was unable to, and accordingly be able to predict with accuracy the future price
movements. The RBF-NN was utilised for both short-term and long-term 
predictions. For short-term forecasting, 
the model was tested over a 5-month horizon, based on the recommendation of the
ARDL model, while the long-term predictions spanned 57 months. 
We differenced the data based on the recommendations of the 
unit root tests conducted earlier to achieve stationarity.

We began by normalising the data, using a z-score normalisation. This is because
neural networks work best with data
that is between a specified range; it ensures that the data is roughly uniformly
distributed between the network inputs and outputs 
(Mendelsohn, 1993, Preprocessing Data for Neural Networks). Following this 
we had to program the RBF-NN into Python. As no specific RBF package exists
in Python, we used the kernel regression approach outlined by 
Bishop, using the GaussianProcessRegressor (GPR) package in Python.

\subsubsection{The Gaussian Process Regressor}

The Scikit GaussianProcessRegressor is based on the 
standard linear regression 
model, equipped with Gaussian noise,

\begin{align} 
    f(x) = x^{T}w, \quad{y = f(x) + \varepsilon}
\end{align}

where $y$ differs from the function values $f(x)$ by noise which is assumed
to follow an independent and identically distributed Gaussian distribution
$\mathcal{N}_1$
\begin{align*}
    \varepsilon \sim \mathcal{N}_1 \bigl(0, \sigma_{n}^2\bigr)
\end{align*}
This assumption together with the model produces the 
probability density of the observations given the inputs, 
which is factored over cases in the training set, 
permissible because of the independence assumption,

\begin{align}
    p(y|X,w) = \prod_{i=1}^{n} p(y_i|x_i ,w) = \mathcal{N}\bigl(X^T, \sigma_{n}^2 I\bigr)
\end{align}

In the Bayesian formalism we need to specify a prior over the parameters, expressing our beliefs about the prior
parameters before we look at the observations. A covariance function or kernel
is specified according to the characteristics of the data; in our model this 
is the generalised inverse multiquadric

$$ k(x,x') = \biggl( ||x-x'|| + \sigma^2\biggr)^{-\beta} $$
and used to construct the covariance matrix $K$, which along with 
a mean of $0$ forms the distribution of the the weights 
$$ w \sim \mathcal{N}\bigl(0, K\bigr)$$
By Bayes' Theorem,

\begin{align}
    p(w|y, X) = \frac{p(y|X,w) p(w)}{p(y|X)}
\end{align}
Using this, the posterior distribution is then obtained

\begin{align}
    p(w|y, X) \sim \mathcal{N}\bigl(\frac{A^{-1}Xy}{\sigma_{n}^{2}}, A^{-1}\bigr)
\end{align}
where the covariance matrix $A^{-1} = K^{-1} + \frac{XX^T}{\sigma_{n}^2}$.
To make predictions on a test case all possible $w$
values, weighted by their posterior probability, are averaged to obtain the
predictive distribution, upon which predicted outputs are computed.

\subsubsection{The Network}

A $4$-dimensional input space $X$
passes inputs $\boldsymbol{\mathrm{x}}_1, \boldsymbol{\mathrm{x}}_2,\ldots \boldsymbol{\mathrm{x}}_{n}$
and corresponding outputs \( y = \{y_1, y_2, \dots, y_n\} \), through the first
of two hidden layers, in which the covariance function $(x,x')$
is applied, the goal being to determine the distribution of the weights. Prior to this,
the optimal hyperparameters in the covariance function, which plays an analogous
role to the RBF basis function, are calculated using GridSearch Cross Validation; these hyperparameters are:
\begin{enumerate}
    \item $\alpha$: a regularisation parameter which represents a small quantity
    that is added to the diagonals of the covariance matrix to ensure it is 
    invertible. 
    \item $\beta$: the power in the covariance function, which controls the shape of the function.
    \item $\sigma$: a parameter which controls how much of the noise in the data the kernel accounts for; naturally, 
    it moderates the risk of overfitting and underfitting.
    \item Length scale: a parameter that controls the influence - analogous to 
    the width each RBF neuron possesses - that each kernel (analogous to node) is to have.
\end{enumerate}
following this the model uses the training observation $(y,X)$ to find
the posterior predictive distribution, and with it the predicted output, after 
averaging over all possible $w$, weighted by their likelihood according to (10).

@@

The model returned a mean absolute error (MAE)  MAE $=0.16$ and 
$R^2 = 9\%$ for the long term prediction.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{short-term.png}
    \caption{}
    \label{fig:}
\end{figure}

The interpretation of this is that, historically, the variations in the 
Consumer Price Index, interest rate, USD/GBP exchange rate, and M3 money 
supply have explained or accounted for $9\%$ of the fluctuations of the
FTSE250 value; in the context of a phenomenon as complex as the stock market,
which is influenced by an inumerable quantity of factors such as investor sentiment
- inherently irrational, 
political instability, geopolitical shocks, corporate governance, and financial regulation, this is 
unsurprising. Furthermore, the selection of economic variables in this study
is by no means exhaustive; commodity prices, international trade dynamics,
economic growth, and many other variables also exert a non-insignificant 
effect on the stock market.

The short-term prediction yielded MAE = $0.07$ and 
$R^2 = 61\%$, for a 5-month time horizon.
The significantly better performance of the model in the short-run
indicates that the selected macroeconomic variables possesses
a stronger predictive power over shorter periods. This was highlighted 
earlier in the ARDL model, with the interest rate and money supply significantly
impacting the FTSE250 price. In the short-term, which we define as 5 months, 
as per the optimum lag for the FTSE250 in the ARDL model, the market movements
are more closely tied to recent deviations in the economy, because theoretically
the short-run is not exposed to the various unforeseen external shocks and structural changes
that dilute the relationship between these variables and the stock market in the long-run.

@@

What did this study achieve: it tested the findings of previous research on the 
UK stock market, via the FTSE250, and was able to...

How may it inform policymakers and investors: the effect of the 
Areas for future work to build upon: consider daily data with some kind of 
stochastic interpolation to get daily data and try other networks. 
Other variables. Autoregress on 
FTSE itself in rbf, as this was not in scope of the project.

\bibliographystyle{plainnat}
\bibliography{references}
